# Noncompliance in Recycling Experiment 

```{problem_description}
Suppose that you want to conduct a study of recycling behavior. A number of undergraduate students are hired to walk door to door and provide information about the benefits of recycling to people in the treatment group. Here are some facts about how the experiment was actually carried out.  

- 1,500 households are assigned to the treatment group. 
- The undergrads tell you that they successfully managed to contact 700 households. 
- The control group had 3,000 households (not contacted by any undergraduate students). 
- The subsequent recycling rates (i.e. the outcome variable) are computed and you find that 500 households in the treatment group recycled. In the control group, 600 households recycled.
```

## Intent to treat effect
What is the ITT? Do the work to compute it, and store it into the object `recycling_itt`.  Provide a short narrative using inline R code, such as `r inline_reference`.

```{r recycling itt, include=TRUE} 
recycling_itt <- 'fill this in'
```

**Answer:** ...

## Compliers average causal effect
What is the CACE? Do the work to compute it, and store it into the object `recycling_cace`.  Provide a short narrative using inline R code.

```{r recycling cace, include=TRUE} 
recycling_cace <- 'fill this in'
```

**Answer:** ...

```{problem_description}
There appear to be some inconsistencies regarding how the undergraduates actually carried out the instructions they were given. 

- One of the students, Mike, tells you that they actually lied about the the number of contacted treatment households and that the true number was 500. 
- Another student, Andy, tells you that the true number was actually 600.
```

## Mike's CACE
What is the CACE if Mike is correct?  Provide a short narrative using inline R code.

```{r cace mike, include=TRUE} 
cace_mike <- 'fill this in'
```

**Answer:** ...

## Andy's CACE 
What is the CACE if Andy is correct? Provide a short narrative using inline R code.

```{r cace andy, include=TRUE}
cace_andy <- 'fill this in'
```

**Answer:** ...

```{problem_description}
For the rest of this question, suppose that **in fact** Mike was telling the truth.  
```

## Effect of false reporting
What was the impact of the undergraduates’s false reporting on our estimates of the treatment’s effectiveness?

**Answer:** ...

## Effect of false reporting... on what quantity?
Does your answer change depending on whether you choose to focus on the ITT or the CACE?

**Answer:** ...



