# Another Turnout Question

```{problem_description}
We are sorry; it is just that the outcome and treatment spaces are so clear! 

This question allows you to scope the level of difficulty that you want to take on. 

- If you keep the number of rows at 100,000 this is pretty straightforward, and you should be able to complete your work on the ischool.datahub. 
- But, the real fun is when you toggle on the full dataset; in the full dataset there are about 4,000,000 rows that you have to deal with. This is too many to work on the ischool.datahub. But if you are writing using `data.table` and use a docker image or a local install either on your own laptop or a cloud provider, you should be able to complete this work. 

Hill and Kousser (2015) report that it is possible to increase the probability that someone votes in the California *Primary Election* simply by sending them a letter in the mail. This is kind of surprising, because who even reads the mail anymore anyways? (Actually, if you talk with folks who work in the space, they will say, "We know that everybody throws our mail away; we just hope they see it on the way to the garbage.")

Can you replicate their findings? Let's walk through them.
```

```{r}
number_of_rows <- 100000
# number_of_rows <- Inf

d <- data.table::fread(
  input = 'https://people.ischool.berkeley.edu/~d.alex.hughes/data/hill_kousser_analysisFile.csv', 
  nrows = number_of_rows)
```

```{problem_description}
(As an aside, you will note that this takes some time to download. One idea is to save a copy locally, rather than continuing to read from the internet. One problem with this idea is that you might be tempted to make changes to this canonical data; changes that would not be reflected if you were to ever pull a new copy from the source tables. One method of dealing with this is proposed by [Cookiecutter data science](https://drivendata.github.io/cookiecutter-data-science/#links-to-related-projects-and-references).)

Here is what is in that data. 

- `age.bin` a bucketed, descriptive, version of the `age.in.14` variable 
- `party.bin` a bucketed version of the `Party` variable 
- `in.toss.up.dist` whether the voter lives in a district that often has close races 
- `minority.dist` whether the voter lives in a majority minority district, i.e. a majority black, latino or other racial/ethnic minority district 
- `Gender` voter file reported gender
- `Dist1-8` congressional and data districts 
- `reg.date.pre.08` whether the voter has been registered since before 2008 
- `vote.xx.gen` whether the voter voted in the `xx` general election 
- `vote.xx.gen.pri` whether the voter voted in the `xx` general primary election 
- `vote.xx.pre.pri` whether the voter voted in the `xx` presidential primary election 
- `block.num` a block indicator for blocked random assignment. 
- `treatment.assign` either "Control", "Election Info", "Partisan Cue", or "Top-Two Info"
- `yvar` the outcome variable: did the voter vote in the 2014 primary election 

These variable names are horrible. Do two things: 

- Rename the smallest set of variables that you think you might use to something more useful. (You can use `data.table::setnames` to do this.) 
- For the variables that you think you might use; check that the data makes sense; 

When you make these changes, take care to make these changes in a way that is reproducible. In doing so, ensure that nothing is positional indexed, since the orders of columns might change in the source data). 

While you are at it, you might as well also modify your `.gitignore` to ignore the data folder. Because you are definitely going to have the data rejected when you try to push it to github. And every time that happens, it is a 30 minute rabbit hole to try and re-write git history. 
```

```{r set names}
setnames(
  x = d,
  old = c("age.in.14", "Party", "Gender", "block.num", "treatment.assign", "yvar"),
  new = c("age",       "party", "gender", "block",     "treatment",        "vote")
)
```

```{r three party labels}
three_party_labeler <- function(x) { 
  party <- ifelse(
    x == 'DEM', 'DEM', 
    ifelse(
      x == 'REP', 'REP', 
      'OTHER'))
  return(party)
}

d[ , three_party := three_party_labeler(party)]
```

```{r treatment factors} 
d[ , treatment_f := factor(treatment)]
d[ , any_letter  := treatment_f != 'Control' ]
```

```{problem_description}
Let us start by showing some of the features about the data. There are `r format(d[, .N], big.mark = ',')` observations. Of these, 
`r format(d[party == 'DEM' , .N], big.mark = ',')` identify as Democrats (`r d[ , mean(party == 'DEM')] * 100` percent); 
`r format(d[party == 'REP', .N], big.mark = ',')`) identify as Republicans (`r d[ , mean(party == 'REP')] * 100` percent); and, 
`r format(d[!(party %in% c('DEM', 'REP')), .N], big.mark = ',')`) neither identify as Democrat or Republican (`r d[ , mean(!(party %in% c('DEM', 'REP')))] * 100` percent). 
```

```{r}
d %>% 
  ggplot() + 
  aes(x = age, color = three_party) + 
  geom_density() + 
  scale_x_continuous(limits = c(17, 100)) + 
  labs(
    title = 'Ages of Party Reporters', 
    subtitle = 'Republicans have more support among older voters', 
    x = 'Age', y = 'Percent of Voters', 
    color = 'Party ID', 
    caption = '"OTHER" include all party preferences, including No Party Preference.'
  ) 

```

## Simple treatment effect 
Load the data and estimate a `lm` model that compares the rates of turnout in the control group to the rate of turnout among anybody who received *any* letter. This model combines all the letters into a single condition -- "treatment" compared to a single condition "control". Report robust standard errors, and include a narrative sentence or two after your code using inline R code, such as `r inline_reference`.  

```{r effect of receiving a letter, message = FALSE, warning = FALSE} 
# Use this block for your work
```

**Answer:** ...

## Letter-specific treatment effects
Suppose that you want to know whether different letters have different effects. To begin, what are the effects of each of the letters, as compared to control? Estimate an appropriate linear model and use robust standard errors. Provide a short narrative using inline R code. 

```{r effect of receiving specific letters, warning = FALSE} 

```

**Answer:** ...

## Test for letter-specific effects 
Does the increased flexibilitiy of a different treatment effect for each of the letters improve the performance of the model? Test, using an F-test. What does the evidence suggest, and what does this mean about whether there **are** or **are not** different treatment effects for the different letters?

```{r f-test}
# anova()
```

**Answer:** ...

## Compare letter-specific effects 
Is one message more effective than the others? The authors have drawn up this design as a full-factorial design. Write a *specific* test for the difference between the *Partisan* message and the *Election Info* message. Write a *specific* test for the difference between *Top-Two Info* and the *Election Info* message. Report robust standard errors on both tests and include a short narrative statement after your estimates. 

```{r specific treatment effects, warning = FALSE}

```

**Answer:** ...

## Count the number of blocks
**Blocks? We don't need no stinking blocks?**  The blocks in this data are defined in the `block.num` variable (which you may have renamed). There are a *many* of blocks in this data, none of them are numerical -- they're all category indicators. How many blocks are there? 

```{r count blocks, include=TRUE}

```

**Answer:** ...

## Add block fixed effects
**SAVE YOUR CODE FIRST** but then try to estimate a `lm` that evaluates the effect of receiving *any letter*, and includes this block-level information. What happens? Why do you think this happens? If this estimate *would have worked* (that's a hint that we don't think it will), what would the block fixed effects have accomplished?

```{r going down with the ship!, eval=FALSE}
##
## SAVE YOUR CODE: before you run the next lines, because it's going 
##                 to crash you if you're on the ischool.datahub.
##                 ... but why does it crash you?
## 
##  Notice that in the chunk declaration, we have set `eval = FALSE`; this is so the code doesn't run until you ask it to.
##
## We'll even write some code that will help.
##   - In the first chain of this data.table, we are scoping only to the columns that we will use in the model;
##   - In the second, we are estimating the model
model_block_fx  <- d[ , .(vote, any_letter, block)][ , lm(vote ~ any_letter + factor(block))]
```

**Answer:** ...

## A clever work-around? 
Even though we can't estimate this fixed effects model directly, we can get the same information and model improvement if we're *just a little bit clever*. Create a new variable that is the *average turnout within a block* and attach this back to the data.table. Use this new variable in a regression that regresses voting on `any_letter` and this new `block_average`. Then, using an F-test, does the increased information from all these blocks improve the performance of the *causal* model? Use an F-test to check. 

```{r alternate approach}

```

**Answer:** ...

## Does cleverness create a bad-control? 
Doesn't this feel like using a bad-control in your regression? Has the treatment coefficient changed from when you didn't include the `block_average` measure to when you did? Have the standard errors on the treatment coefficient changed from when you didn't include the `block_average` measure to when you did? Why is this OK to do?

```{r compare models}
# stargazer(
#   fill in with your models
#   type = 'text'
# )
```

**Answer:** ...

```{r plot assessing good/bad control, include=FALSE}
setkeyv(x = d, cols = 'block')

d[block > 0 , .(
      prop_control  = mean(treatment_f == 'Control'), 
      prop_info     = mean(treatment_f == 'Election info'), 
      prop_top_two  = mean(treatment_f == 'Top-two info'), 
      prop_partisan = mean(treatment_f == 'Partisan')), 
    keyby = .(block)] %>% 
  melt(data = ., id.vars = 'block') %>% 
    ggplot() + 
      aes(x = block, y = value, color = variable) + 
      geom_point() + 
      facet_wrap(facets = vars(variable), nrow = 2, ncol = 2, scales = 'free')
```
